Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-09 p2/axioms.tex
Minor improvements

\myskip
Our aim is to derive information about the effects of sequences
of commands independently of the actual filesystems.
In order to make this possible, we investigate the smallest building
blocks of sequences: pairs of commands that act on a filesystem directly one after the other.
This approach is useful as there are a limited number of command pairs,
because, as we argued above, we can disregard the exact output values of commands apart from their type,
and we can also abstract the relationship between the nodes in the two commands
to a finite number of cases.
These properties of command pairs are crucial as they determine
how a set of commands can be re-ordered to be applied to a filesystem
during synchronization, and what command pairs will never be compatible.

\myskip
Command pairs in general have the form
\[ \cxynv\cc  \czwmv \]
where $x,y,z,w\in\setv$ and $n,m\in\setn$. 
Extending \cref{def:command_categories}, we call certain pairs
\emph{construction} or \emph{destruction pairs}.

>>>>

\myskip
One aim of our algebraic model is to
derive as much information about the effects of sequences
of commands independently of the actual filesystems as possible.
In order to make this possible, we investigate the smallest building
blocks of sequences: pairs of commands that act on a filesystem directly one after the other.
This approach is useful as there are a limited number of command pairs,
because, as we argued above, we can disregard the exact output values of commands apart from their type,
and we can also abstract the relationship between the nodes in the two commands
to a finite number of cases.
These properties of command pairs are crucial as they determine
how a set of commands can be re-ordered to be applied to a filesystem
during synchronization, and what command pairs will never be compatible.

Command pairs in general have the form
\[ \cxynv\cc  \czwmv \]
where $x,y,z,w\in\setv$ and $n,m\in\setn$. 
Extending \cref{def:command_categories}, we call certain pairs
\emph{construction} or \emph{destruction pairs}.

### 2018-07-09 p2/def-commands.tex
Minor improvements

\myskip
For reasons also listed in \cite{NREC}, in this paper we will not consider
a \textit{move} or \textit{rename} command.
This turns out to be useful because this would be the only command that affects
filesystems at two nodes at once, therefore describing 
the dependencies for \textit{move} would call for a more complicated model.
From a pragmatic perspective, this restriction does not mean that in an application
implementing conflict resolution using the algorithm described here would not be
able to handle renames by pre- and post-processing changes in the filesystem to
discover them, which can enhance usability, but which
(especially when a rename is combined with changes to the content)
is a non-trivial problem in itself.

>>>>

\myskip
For reasons also listed in \cite{NREC}, in this model we will not consider
a \textit{move} or \textit{rename} command.
This turns out to be useful because this would be the only command that affects
filesystems at two nodes at once, therefore describing 
the dependencies for \textit{move} would call for a more complicated model.
As \cref{sec_multidir} details, this restriction does not mean that in an application
implementing conflict resolution using the algorithm described here would not be
able to handle renames by pre- and post-processing changes in the filesystem to
discover them, which can enhance usability.
